Visual Inference for Goodness-of-Fit for A Network Model

### 2017-09-27 ASApaper/paper.Rmd
discussion in paper

@@

>>>>

The most significant effect was the jumping transitive triplet (JTT) parameter for the party covariate, which was estimated to be about -6 with a standard error of 0.11. This effect relies on the number of transitive closures formed between two senators from different parties. Due to the divisive nature of American politics, the party effect is dominant. Another significant effect was the same JTT parameter for the sex covariate, with an estimate of about 3 with a standard error of 0.89. Another significant effect was the covariate-related similarity score-weighted transitive triplets for the number of bills authored by a senator. This effect was estimated at about 10 with standard error of 3.9, and the high positive effect suggests senators tend to collaborate with other senators who author about the same number of bills they do.

@@

# Exploratory plots

```{r M1}
M1senateEsts <- read_csv("../Data/senate/basicModelFitsSenate1000.csv")
inisdSenateEsts <- read_csv("../Data/senate/inisdModelFitsSenate1000.csv")
jttpSenateEsts <- read_csv("../Data/senate/jttpModelFitsSenateAll1000.csv")
jttsSenateEsts <- read_csv("../Data/senate/jttsModelFitsSenateAll1000.csv")
# ggpairs(M1senateEsts, columns = 1:8)
# M1senateEsts %>% mutate(converged = (maxConv <= 0.25)) %>% 
#   ggplot() + 
#   geom_density(aes(x = density, color = converged), adjust = .5) 
# M1senateEsts %>% mutate(converged = (maxConv <= 0.25)) %>% 
#   ggplot() + 
#   geom_histogram(aes(x = density, color = converged), binwidth = .005, fill = NA) + facet_wrap(~converged)

# make ests long - M1
M1senateEsts %>% 
  select(Rate:recip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:recip) -> melt1 
M1senateEsts %>% 
  select(se_density:sim) %>% 
  gather(parameter, se, se_density:se_recip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> M1SenEstsLong

# make ests long - inisd
inisdSenateEsts %>% 
  select(Rate:inIsDegree, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:inIsDegree) -> melt1 
inisdSenateEsts %>% 
  select(se_density:sim) %>% 
  gather(parameter, se, se_density:se_inIsDegree) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> inisdSenEstsLong

# make ests long - jttp
jttpSenateEsts %>% 
  select(Rate:jumpXTransTrip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:jumpXTransTrip) -> melt1 
jttpSenateEsts %>% 
  select(se_density:maxConv, sim) %>% 
  gather(parameter, se, se_density:se_jumpXTransTrip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> jttpSenLong

# make ests long - jtts
jttsSenateEsts %>% 
  select(Rate:jumpXTransTrip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:jumpXTransTrip) -> melt1 
jttsSenateEsts %>% 
  select(se_density:maxConv, sim) %>% 
  gather(parameter, se, se_density:se_jumpXTransTrip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> jttsSenLong

```
